---
title: "1_dataclean_mc_fall"
author: "Karin Emanuelson"
date: "11/15/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## Setup
knitr::opts_knit$set(root.dir='./..')
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(xts)
library(dygraphs)
library(ggrepel)
library(knitr)
library(plotly)
library(ggthemes)
library(RColorBrewer)
library(htmltools)
library(chron)

```

##ENSURE SPREADSHEET IS FILTERED FIRST RUN_DATE (oldest to newest) then by DATETIME (oldest to newest)

```{r, include=FALSE}
# read in Conductivity data for 350 and 450
cond_cl3<-read_csv('data/in/CZO3Calibrate_curve.csv')[, 2:5] %>%
  mutate(datetime = mdy_hm(datetime, tz = 'MST7MDT')) %>%
  mutate(site = '350')%>%
  mutate(Cond_Cl = NaCl * 0.6067)%>%
  select(datetime, site, Cond_Cl)
cond_cl4<-read_csv('data/in/CZO4Calibrate_curve.csv')[, 2:5] %>%
  mutate(datetime = mdy_hm(datetime, tz = 'MST7MDT')) %>%
  mutate(site = '450')%>%
  mutate(Cond_Cl = NaCl * 0.6067)%>%
  select(datetime, site, Cond_Cl)
cond_cl50<-read_csv('data/in/CZO50Calibrate_curve.csv')[, 2:5] %>%
  mutate(datetime = mdy_hm(datetime, tz = 'MST7MDT')) %>%
  mutate(site = '50')%>%
  mutate(Cond_Cl = NaCl * 0.6067)%>%
  select(datetime, site, Cond_Cl)


cond_cl<-rbind(cond_cl3, cond_cl4, cond_cl50)

## Load Raw Chem Data for Main Channel Samples
chem_grab_mc<- read_csv(('data/in/2018_ComoCreek_WaterChemistry_Mastersheet_Recreated_11719_SORTED.csv'), skip=7)%>%
      mutate(Datetime= mdy_hm(Datetime,tz='MST7MDT'))%>%
      mutate(run_date= mdy(run_date))%>%
      select(-ID)%>%
      # mutate(id = rownames(.))%>%
  select(
    sample = "Sample #" ,
    # id,
    site = Location,
    datetime = Datetime,
    compartment = Type1,
    sample_type = Type2,
    rundate = run_date,
    df = DF,
    Na:SO4_DIL
  )%>%
    filter(compartment == 'MC') %>%
  filter(sample_type  %in% c('MC', 'MC DUP', 'MC DIL'))%>%
  left_join(cond_cl, by=c("datetime", "site"))

chem_mc_cond<-chem_grab_mc%>%
  select(sample:df, Cond_Cl)%>%
  mutate(df = 1)%>%
  gather(var, value, Cond_Cl) %>%
  filter(value != 0)%>%
  mutate(rundate = mdy('01-01-1990'))%>%
  mutate(conc_type = 'cond') %>%
  mutate(MaxDL_flag = 'NA') %>%
  mutate(MDL_flag= 'NA')%>%
  mutate(id= 'NA')

#Load raw DOC samples
chem_mc_doc<-read_csv(('data/in/2018_ComoCreek_WaterChemistry_Mastersheet_DOC.csv'), skip=6)%>%
    select(
    sample = "Sample #" ,
    DOC
  )

chem_doc_gather<-left_join(chem_grab_mc, chem_mc_doc, by="sample")%>%
    select(sample:df,DOC)%>%
    mutate(df = 1)%>%
    gather(var, value, DOC)%>%
    filter(value != 0)%>%
    mutate(conc_type = 'prelim') 

## NEED TO UPDATE MAXDL for DOC
# lookup table for chem Max/Min
chem_qc= data.frame(var = c('Cl','NO3','PO4','DOC'), MaxDL=c(1.7, 5, 7.5, 50), MDL=c(.01, .01, .01, .05))
```

## Clean data: Look at sample concentrations for each day. Select which value from different run (out of the series of duplicate and dilution runs)


```{r, include=FALSE}
### Create long dataset
chem_mc<-chem_grab_mc %>%
  select(sample:SO4)%>%
  gather(var, value, Na:SO4) %>%
  filter(var %in% c('NO3','Cl','PO4'))%>%
  mutate(value = as.numeric(value))%>%
  mutate(site = as.numeric(site))%>%
  mutate(df = if_else(is.na(df),1,df))%>%
  mutate(conc_type = 'final') %>%
  mutate(value = if_else(is.na(value), .005, value))%>%
  rbind(chem_doc_gather)%>%
  mutate(id = rownames(.))

chem_flag<- 
  chem_mc%>%
  mutate(value = value/df)%>%
  mutate(conc_type='raw')%>%
  left_join(chem_qc)%>%
  mutate(MaxDL_flag = if_else(value>MaxDL, 'Yes','No'))%>%
  mutate(MDL_flag= if_else(value<MDL, 'Yes','No'))%>%
  select(id, var, MaxDL_flag, MDL_flag)
  
chem_long_mc<-
  chem_mc%>%
  left_join(chem_flag)%>%
  rbind(chem_mc_cond)%>%
  mutate(id = rownames(.))

cond_cl_long<-chem_long_mc%>%
  filter(sample_type=="MC")%>%
  filter(site!="50")%>%
  filter(var=="Cond_Cl")%>%
  mutate(date=date(datetime))
```


```{r, include = FALSE}
### Define functions to graph data and set color scheme
plotChem <- function (df, choose_param=c( 'Cl', 'NO3', 'PO4', 'DOC', 'Cond_Cl'), loc ='350', w = 1200, h =    1000) {
  date_title<-date(df$datetime[[1]])
  # df_fil<-filter(df, site == loc)
  ggplotly(
    ggplot(
      dplyr::filter(df, site==loc, var %in% choose_param),
      aes(
        datetime,
        value,
        fill = c(sample_type),
        text = paste('date: ',datetime,
          '<br> value:',value,
          '<br> sample_type:',sample_type,
          '<br> rundate:',rundate,
          '<br> sample:',sample,
          '<br> site:',loc,
          '<br> df:',df,
          '<br> MaxDL_flag:',MaxDL_flag,
          '<br> MDL_flag:',MDL_flag,
          '<br> id:',id
        ),
        group = 1
      )
    ) +
      geom_point(shape = 21, size = 3) +
      geom_line() +
      theme_few() +
      scale_fill_manual(values = col_vector) +
      facet_wrap( ~ var, ncol = 1, scale = 'free_y')+
      labs(title = date_title),
    width = w,
    height = h,
    tooltip = 'text'
  )
}

#create color scheme for chem plots
n <- 40
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))

```

## 350
### Raw Visualize
```{r, echo = FALSE}
# Filter for each injection
injdates<-ymd(c('2018-06-26','2018-06-28', '2018-06-30', '2018-07-02', '2018-07-17' , '2018-07-19', '2018-07-21', '2018-07-23'))
chem_grab_nest_mc<-chem_long_mc%>%
  mutate(date=date(datetime))%>%
  filter(date %in% injdates)%>%
  arrange(date)%>%
  group_by(date)%>%
  nest()

mc<-map(chem_grab_nest_mc$data, loc='350', plotChem)

mc[[1]]
mc[[2]]
mc[[3]]
mc[[4]]
mc[[5]]
mc[[6]]
mc[[7]]
mc[[8]]

```

#### Create good_id vector for site 350
```{r}
# Points to background correct
good_id_mc3_bg<-c(68:75, 925:932, 236:238, 2818:2820, 1093:1095, 265:268, 1122:1123, 1979:1982, 280:283, 2884:2887, 1137:1140, 1994:1997, 665:670, 1522:1527, 145:149, 2721:2725, 1002:1006, 694, 695, 697, 795, 1551, 1552, 1554, 1652, 163, 164, 166, 167, 2739:2741, 2743, 1020:1024, 1877:1879, 1881, 2408, 2409, 2411, 2509 )#350

good_id_mc3_fall<-c(291:293, 295, 297, 299, 302, 305, 307, 933:936, 1061:1065, 351, 352, 354, 356, 358, 360, 362, 429, 366, 368, 370, 2821:2832, 1096:1107, 373:379, 381, 382, 390, 391, 1126:1136, 1983:1993, 392, 394, 395, 397, 399, 401:403, 349, 350, 2889, 2891:2895, 2967, 2970, 2971, 2974, 2975, 1141:1146, 1201, 1203, 1204, 1206, 1207, 1998:2003, 2058, 2060, 2061, 2063, 2064, 671:681, 1641:1651, 627:635, 438, 624, 625, 626,629:635, 2726:2738, 1007:1019, 700, 701, 703, 704, 711,714, 717:724, 638:641, 663, 664, 810:814, 2747,2766:2775, 1028, 1047:1056, 1885, 1904:1913, 1653:1666, 2510:2523, 2538) #350

```

## 450
### Raw Visualize
```{r, echo = FALSE}
# Filter for each injection
injdates<-ymd(c('2018-06-26','2018-06-28', '2018-06-30', '2018-07-02', '2018-07-17' , '2018-07-19', '2018-07-21', '2018-07-23'))
chem_grab_nest_mc<-chem_long_mc%>%
  mutate(date=date(datetime))%>%
  filter(date %in% injdates)%>%
  arrange(date)%>%
  group_by(date)%>%
  nest()

mc4<-map(chem_grab_nest_mc$data, loc='450', plotChem)

mc4[[1]]
mc4[[2]]
mc4[[3]]
mc4[[4]]
mc4[[5]]
mc4[[6]]
mc4[[7]]
mc4[[8]]

```

#### Create good_id vector for site 450
```{r, echo = FALSE}
# Points to background correct
good_id_mc_bg<- c(good_id_mc3_bg, 200:203, 222:224, 1057, 1058, 1060, 1079:1081, 235, 251, 252, 2817, 2834, 2836, 1092, 1108, 1109, 322:324, 1179:1181, 2036:2038, 337:340, 3147, 3149, 3151, 3153, 1194:1197, 2197:2200, 642:644, 1499:1501, 174:177, 2750:2753, 1031:1034, 520:524, 1377:1381, 2234:2238, 209, 211, 212, 1066, 1068, 1069, 2790, 2792, 2793, 1923:1926) #450

good_id_mc_fall<-c(good_id_mc3_fall, 818, 820, 821, 300, 301, 303, 304, 306, 308, 309, 1082:1091, 353, 355, 357, 359, 361, 363, 364, 365, 367, 369, 371, 372, 2838, 2840, 2842, 2844, 2846, 2848, 2850, 2852, 2854, 2856, 2858, 2860, 1110:1121, 577, 383:389, 335, 336, 1182:1193, 2039:2050, 393, 398, 400, 404, 405:410, 3155, 3157, 3159, 3161, 3163, 3165, 3167,  3169, 3171, 3173, 3536, 1198:1200, 1202, 1205, 1349: 1353, 1711, 2201, 2202:2210, 2568, 645:653, 1693:1701, 822, 823, 656:662, 2754:2762, 1035:1043, 593, 592:600, 602, 1382:1385, 1390:1396, 2239:2242, 2247:2250, 2252, 2253, 827:835, 3518:3526, 1070:1078, 2541:2549) #450

good_id_mc<- c(good_id_mc_bg, good_id_mc_fall)
```

## Create dataset with selected points
```{r, echo = FALSE}
#create dataset selected background points
chem_clean_mc_bg <- chem_long_mc%>%
  filter(id %in% good_id_mc_bg)%>%
  mutate(date=date(datetime))

#create a dataset of selected points
chem_clean_long_mc <- chem_long_mc%>%
  filter(id %in% good_id_mc)%>%
  mutate(date=date(datetime))

chem_clean_graph_mc<-  rbind(chem_clean_long_mc, cond_cl_long)

#double check that Max Detection Limit is vaild
chem_clean_long_flagged<-chem_clean_long_mc%>%
  filter(MaxDL_flag== 'Yes')

count(chem_clean_long_flagged)
```

## 350
### Visualize Selected Data
```{r, echo=FALSE}
# Double check everything
chem_clean_nest_mc<-chem_clean_graph_mc%>%
  filter(date %in% injdates)%>%
  arrange(date)%>%
  group_by(date)%>%
  nest()


c3<-map(chem_clean_nest_mc$data, loc='350', plotChem)
# df<-chem_clean_nest_mc$data
c3[[1]]
c3[[2]]
c3[[3]]
c3[[4]]
c3[[5]]
c3[[6]]
c3[[7]]
c3[[8]]
```

## 450
### Visualize Selected Data
```{r, echo = FALSE}
c4<-map(chem_clean_nest_mc$data, loc='450', plotChem)

c4[[1]]
c4[[2]]
c4[[3]]
c4[[4]]
c4[[5]]
c4[[6]]
c4[[7]]
c4[[8]]
```


```{r, include = FALSE}
### export for UNM team
# # data for UNM
# library(chron)
# 
# cl_conc<-chem_clean_long_mc%>%
#   filter(site == '450')%>%
#   filter(date %in% ymd(c('2018-07-17' , '2018-07-19')))%>%
#   filter(var =='Cl')%>%
#   filter(MaxDL_flag == 'No')
# 
# cl_times<-times(format(cl_conc$datetime, "%H:%M:%S"))
# 
# cl_final<-cbind(cl_conc, cl_times)
# 
# write_csv(cl_final,"data/out/cl_071718_071918_csu_ic-times.csv" )

```



### Summarize to get mean BG conc per day
```{r, echo = FALSE}
chem_mean_mc_bg<- chem_clean_long_mc%>%
  filter(id %in% good_id_mc_bg)%>%
  mutate(date=date(datetime))%>%
  group_by(date, var, site)%>%
  summarize(bg_mean=mean(value))

background_means_mc<-chem_mean_mc_bg%>%
    spread(var, bg_mean)
background_means_mc

write_csv(background_means_mc,"data/in/background_means_mc.csv" )
```

## Clean up data and write csv for final graphs
```{r}

 chem_final<- chem_clean_graph_mc%>%
   mutate(datetime_MDT= as.POSIXct(datetime,tz='MST7MDT'))%>%
   mutate(raw_value_ppm=value)


 chem_final_order<- chem_final%>%
   select("sample", "site", "date", "datetime", "compartment", "sample_type","rundate", "id", "df","var", "MaxDL_flag", "MDL_flag",  "raw_value_ppm")
 
 
corr_times<-times(format(chem_final$datetime, "%H:%M:%S"))
chem_final_form<-cbind(chem_final, corr_times)


write.csv(chem_final_order,"data/out/chem_como.csv", row.names=FALSE)
```


### Background correct falling limb sample concentrations. - NOT ANYMORE

```{r, echo = FALSE, message=FALSE, warning = FALSE}
# #create dataset with bg_mean concentrations
# chem_merge<- chem_clean_long_mc%>%
#   left_join(.,chem_mean_mc_bg)
# 
# # Subtract bg from raw value
# library(chron)
# chem_corr<- chem_merge%>%
#   mutate(value_corr=value-bg_mean)%>%
#   mutate(datetime_MDT= as.POSIXct(datetime,tz='MST7MDT'))%>%
#   mutate(raw_value_ppm=value)%>%
#   mutate(bg_mean_ppm=bg_mean)%>%  
#   mutate(value_corr_ppm=value_corr)
# 
# chem_corr_order<- chem_corr%>%
#   select("sample", "site", "date", "datetime", "compartment", "sample_type","rundate", "id", "df","var", "MaxDL_flag", "MDL_flag",  "raw_value_ppm", "bg_mean_ppm","value_corr_ppm")
# 
# # corr_times<-times(format(chem_corr$datetime, "%H:%M:%S"))
# # corr_final<-cbind(chem_corr, corr_times)
# 
# 
# write.csv(chem_corr_order,"data/out/chem_bg_corrected.csv", row.names=FALSE)
# 
# #Create function to graph
# plotChem_corr <- function (df, loc, value = value_corr) {
#   date_title<-date(df$datetime[[1]])
#       ggplot(dplyr::filter(df, site==loc), aes(datetime, value_corr),group = 1) +
#       geom_point(shape = 16, size = 3) +
#       geom_line() +
#       theme_few() +
#       facet_wrap( ~ var, ncol = 1, scale = 'free_y')+
#       labs(title = date_title)
# }
# 
# chem_corr_nest<-chem_corr%>%
#     # filter(date %in% injdates)%>%
#   arrange(date)%>%
#   group_by(date)%>%
#   nest()
```

## Visually inspect background corrected falling limb sample concentrations for each day.
```{r}
# #Create function to graph
# plotChem_corr <- function (df, loc, value = value_corr) {
#   date_title<-date(df$datetime[[1]])
#   loc_title<-paste(loc, date_title, sep=": ")
#       ggplot(dplyr::filter(df, site==loc), aes(datetime, value),group = 1) +
#       geom_point(shape = 16, size = 3) +
#       geom_line() +
#       theme_few() +
#       facet_wrap( ~ var, ncol = 1, scale = 'free_y')+
#       labs(title = loc_title)
#       }
```

### Graph site 350
```{r, echo = FALSE}
# corr3<-map(chem_clean_nest_mc$data, plotChem_corr, loc='350', value=chem_clean_nest_mc$data$value )
# 
# corr3[[1]]
# corr3[[2]]
# corr3[[3]]
# corr3[[4]]
# corr3[[5]]
# corr3[[6]]
# corr3[[7]]
# corr3[[8]]


```

### Graph Site 450
```{r, echo = FALSE}
# corr4<-map(chem_corr_nest$data, plotChem_corr, loc='450', value =chem_corr_nest$data$value_corr )
# 
# corr4[[1]]
# corr4[[2]]
# corr4[[3]]
# corr4[[4]]
# corr4[[5]]
# corr4[[6]]
# corr4[[7]]
# corr4[[8]]
```


